---
title: "mapscanner styles"
author: "Mark Padgham"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: true
        number_sections: false
        theme: flatly
vignette: >
  %\VignetteIndexEntry{mapscanner styles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r pkg-load, echo = FALSE, message = FALSE}
library (mapscanner)
```

The `mapscanner` package is able to generate maps in the [three styles provided
by mapbox](https://docs.mapbox.com/api/maps/#styles). [The `ms_generate_map()`
function](https://docs.ropensci.org/mapscanner/reference/ms_generate_map.html)
has a `bw` parameter with a default of `TRUE` to generate black-and-white maps,
including conversion of coloured mapbox styles to black-and-white. The use of
coloured maps, generated with `bw = FALSE`, is not generally recommended in
`mapscanner`, and overdrawn markings are identified exclusively by colour, and
any markings in a colour which is also present in the underlying maps will
generally not be accurately identified.

Because illustrations of these map styles requires files too large to be placed
inside an R package, they are not included with this vignette. The styles can
nevertheless be easily examined from [the main mapbox styles
page](https://docs.mapbox.com/api/maps/styles/), or by clicking the hyperlinked
text below, and are:

1. `style = "light"` - the generally recommended style for `mapscanner`,
   ["designed to provide geographic context while highlighting the data on your
   analytics dashboard, data visualization, or data
   overlay](https://www.mapbox.com/maps/light/).
2. `style = "streets"`, which is,
   ["a comprehensive, general-purpose map that emphasizes accurate, legible
   styling of road and transit networks](https://www.mapbox.com/maps/streets/).
3. `style = "outdoors"`, which is, ["a general-purpose map with curated
   tilesets and specialized styling tailored to hiking, biking, and the most
   adventurous use cases"](https://www.mapbox.com/maps/outdoors/).

Alternatively, these different styles can be examined for any desired area with
the following code.

```{r map-gen, eval = FALSE}
bb <- osmdata::getbb ("<name of location>")
shrink <- 0.3 # shrink that bounding box to 30% size
bb <- t (apply (bb, 1, function (i)
                 mean (i) + c (-shrink, shrink) * diff (i) / 2))

ms_generate_map (bbox = bb,
                 max_tiles = 16L,
                 mapname = "map-light",
                 style = "light")
ms_generate_map (bbox = bb,
                 max_tiles = 16L,
                 mapname = "omaha-streets",
                 style = "streets",
                 bw = FALSE)
ms_generate_map (bbox = bb,
                 max_tiles = 16L,
                 mapname = "omaha-outdoors",
                 style = "outdoors",
                 bw = FALSE)
```
